### 2015-01-16 publishing/plos_template.tex
added caption for pcr data and fixed figure labels
added chracterization methods and cell culture title updated outline

@@

\begin{figure}
\includegraphics[scale=0.05]{../presentation-figures/24well.JPG} % remove for manuscript submission
\includegraphics[scale=0.05]{../presentation-figures/printed-network.JPG} % remove for manuscript submission
\caption{
{\bf Photographs of the printed device.}  The printed device with membranes adhered. The distribution network is printed completely in resin.
}
\label{Figure_label}
\end{figure}

\begin{figure}
\includegraphics[scale=0.3]{../presentation-figures/6-well-plot.png} % remove for manuscript submission
\includegraphics[scale=0.3]{../presentation-figures/24-well-plot.png} % remove for manuscript submission
\caption{
{\bf Oxygen Characterization.}  Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device. Each 6 well row of the plate can be controlled independently.  
}
\label{Figure_label}
\end{figure}

>>>>

\subsection*{Oxygen characterization}

Oxygen was measured with PtOEPK planar sensors that were fixed to the bottom of a 24well plate. 
The intensity of the sensor was measured and corellated to the concentration of oxygen with Stern-Volmer analysis.
Gas was perfused through the device with negitave pressure to eliminate bubbles.
The inlet tubing was placed in a cone with with a flow that exceded the vacuum flow rate.
All gas tanks used in the oxygen characterization were 5\% CO2 in addition to the desired gas mix in anticipation of cell culture experiments.

\subsection*{Cell culture and hypoxia assay}

@@

\begin{figure}
\includegraphics[scale=0.05]{../presentation-figures/24well.JPG} % remove for manuscript submission
\includegraphics[scale=0.05]{../presentation-figures/printed-network.JPG} % remove for manuscript submission
\caption{
{\bf Photographs of the printed device.}  The printed device with membranes adhered. The distribution network is printed completely in resin.
}
\label{device-photos-figure}
\end{figure}

\begin{figure}
\includegraphics[scale=0.3]{../presentation-figures/6-well-plot.png} % remove for manuscript submission
\includegraphics[scale=0.3]{../presentation-figures/24-well-plot.png} % remove for manuscript submission
\caption{
{\bf Oxygen Characterization.}  Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device. Each 6 well row of the plate can be controlled independently.  
}
\label{oxygen-char-figure}
\end{figure}

\begin{figure}
%\includegraphics[scale=0.2]{image.jpg} % remove for manuscript submission
\caption{
{\bf PCR Data.}  Not finished yet.  
}
\label{pcr-data}
\end{figure}
